% ============================================================
% APPENDIX B: AI USAGE
% ============================================================
% Document how AI tools were used in this project.
% Required by the project spec and UCT guidelines.
% ============================================================

\section{AI Usage}
\label{app:ai}

In accordance with UCT guidelines on the use of artificial intelligence in academic
work, this appendix documents all AI tools employed during this project and the manner
in which they were used.

\paragraph{Tools used.}
\begin{itemize}
    \item \textbf{[Tool name, version, provider]}: used for \ldots
    % TODO: list each AI tool with version and approximate dates of use.
\end{itemize}

\paragraph{Code assistance.}
AI tools were used to suggest implementations of \ldots\ and to assist with
debugging \ldots\ All AI-generated code was reviewed critically, tested against
closed-form Black--Scholes prices and deltas, and modified where necessary. We take
full responsibility for the correctness of the final code.

\paragraph{Writing assistance.}
AI was used to \ldots\ All text in this paper represents the authors' own understanding
and has been substantially written or rewritten by the authors.

\paragraph{Literature search.}
AI tools were consulted to suggest relevant papers. All suggested references were
independently verified on Google Scholar or the publisher's website before citation.

\paragraph{Compliance statement.}
No AI tool was granted autonomous access to submission systems or data. All outputs
of this project --- including the code, results, and written analysis --- represent
the authors' own work and conclusions.
